%!TEX root = ./main.tex

\section{Primal-Dual Framework for Packing Constraints}		\label{sec:packing}

\subsection{Formulation.}

\begin{align*}
\max  \sum_{t} &a^{t} x^{t} \\
\sum_{t} b_{i}^{t} x^{t} &\geq 1 & &  \forall 1 \leq i \leq m \\
x^{t} &\in \{0,1\} & & \forall t
\end{align*}

We formalize the problem differently. At the arrival of variable $x^{t}$ (that we need to set as 0 or 1), for a given parameter $M > 0$, we try to achieve
$\sum_{t} a^{t} x^{t} \geq M(t)$ while minimizing the violation in the packing constraints, i.e., minimize $\max_{1 \leq i \leq m} \sum_{t} b_{i}^{t} x^{t}$, especially when
the latter is larger than 1. Subsequently, one can use binary search to find the largest $M$ so the violation is not far from 1.
That can be formalized as follows (up to a constant factor due to the connection between the $\ell_{\infty}$-norm and $\ell_{\log m}$-norm).
%
\begin{align*}
\min ~ \biggl \| \biggl( \sum_{t} b_{1}^{t} x^{t}, \ldots, &\sum_{t} b_{m}^{t} x^{t} \biggr) \biggr \|_{\log m}  \\
\sum_{t} a^{t} x^{t} &\geq \frac{M(t)}{8\ln(n/\eta)}  \\
x^{t} &\in \{0,1\} ~ \forall t
\end{align*}
%
This is a convex covering problem that we can solve using the previous framework.

\begin{theorem}
abc
\end{theorem}
%
\begin{proof}
Fix a parameter $M(t)$. The algorithm provides a solution $\vect{x}$ such that for any feasible solution $\vect{x}'$
(i.e., $\sum_{t} a^{t} (x')^{t} \geq \frac{M(t)}{8\ln(n/\eta)}$), it holds that
$8\ln(n/\eta) f(\vect{x}') \geq f(\vect{x})$.
Assume that there exists an arbitrary vector $\vect{y}$
achieving a profit of $2M(t)$, i.e.,  $\sum_{t} a^{t} y^{t} \geq 2M(t))$.
We have
$$
f(\vect{y}) =  8\ln(n/\eta) \cdot f\biggl(\frac{\vect{y}}{8\ln(n/\eta)}\biggr) \geq
8\ln(n/\eta) \frac{f\bigl( \vect{x}\bigr)}{8\ln(n/\eta)} = f(x) > 1
$$
where the first equality holds since the multiplicative property of norms, the inequality is due to the aforementioned observation
(note that $\frac{\vect{y}}{8\ln(n/\eta)}$ satisfies the constraint $\sum_{t} a^{t} \frac{y^{t}}{8\ln(n/\eta)} \geq \frac{M(t))}{8\ln(n/\eta)}$).
It implies that there exists $1 \leq i \leq m$ such that $\sum_{t} b_{i}^{t} x^{t} > 1$ and so $\vect{y}$ is infeasible to the packing problem.
Therefore, all solutions satisfying the packing constraints have profit at most $M(t)$. The theorem follows.
\end{proof}


\subsubsection*{Algorithm.}


\begin{algorithm}[!ht]
	\begin{algorithmic}[1]
	\STATE Initially, set $A^* \gets \emptyset$ \ \ \texttt{(where $A^*$ is the solution set and $\forall e \in A^* : x_{e} = 1$)}
	\STATE All primal and dual variables are initially set to 0
	\STATE During every step, for each feasible solution $S$, $z_{S} = \prod_{e \in S} x_{e} \prod_{e \notin S} (1 - x_{e})$ is maintained.
	\STATE Let $\tau$ be the continuous timer during the execution of the algorithm.
	\FOR{each time $t$, for the new primal constraint $\sum_{e} a_{e}^{t} x_{e} \geq 1$
	and dual variable $\alpha^{t}_{A^*}$}
		\WHILE[\texttt{Increase primal, dual variables}]{$\sum_{e \notin A^{*}} b^{t}_{e}(A^{*})\ x_{e} < 1$}
			\STATE Increase $\tau$ with a rate of $1$.
			\STATE Increase $\alpha^{t}_{A^{*}}$ at rate $1\ /\ (\lambda \ \ln(1+2d^{2}/\eta))$
			%(Note that $c_{k,A^{*}} > 0$ by the condition of the while loop.)
			\label{algo-covering:alpha}
			\FOR{$e \notin A^{*}$ such that $b^{t}_{e}(A^{*}) > 0$}
				\STATE \textbf{if} $\beta_{e} <  \frac{1}{\lambda} \nabla_{e} F(\vect{x})$ \textbf{then}
				$\beta_{e} \gets \frac{1}{\lambda} \nabla_{e} F(\vect{x})$
				\label{algo-covering:beta}
				\STATE Increase $x_{e}$ at a rate according to the following
				\begin{align*}
					\frac{\partial x_{e}}{\partial \tau}	\gets
					\frac{b^{t}_{e}(A^{*}) \ x_{e}}{\lambda \beta_{e}} + \frac{\eta}{\lambda \beta_{e} d}
					+ \frac{(1 - \eta) \cdot \one_{\{pred(x_{e}) = 1\}}}{\nabla_{e} F(\vect{x}) \cdot |\{e': pred(x_{e'}) = 1,\ b^{t}_{e'}(A^{*}) > 0\}| }
				\end{align*}
				\label{algo-covering:x}
			\ENDFOR
			\STATE \textbf{if} $x_{e} = 1$ \textbf{then} $A^{*} \gets A^{*} \cup \{e\}$
			\FOR[\texttt{Decrease dual variables}]{$e : e \notin A^*$} \label{algo-decrease}
				\WHILE{
					$\sum_{t'=1}^{t} \sum_{A: e \notin A} b^{t'}_{e}(A) \ \alpha^{t'}_{A} > \beta_{e}$}
						\FOR{$(t_{e}^{*}, A) \textnormal{ such that } b^{t_{e}^{*}}_{e}(A) =  \max \{b^{t'}_{e}(A)\ |\ \forall A: e \notin A \textnormal{ and }\forall t' \leq t \textnormal{ s.t. } \alpha^{t'}_{A} > 0\}$} \label{algo-covering:bmax}
							\STATE Decrease $\alpha^{t_{e}^{*}}_{A}$ continuously with a rate of
							$\frac{b^{t}_{e}(A^{*})}{b^{t_{e}^{*}}_{e}(A)} \cdot\frac{1}{\lambda \cdot \ln(1+2d^{2}/\eta)}$
							\label{algo-covering:decrease}
					\ENDFOR
				\ENDWHILE
			\ENDFOR
		\ENDWHILE
	\ENDFOR
	\end{algorithmic}
	\caption{Online Algorithm for Non-Linear Covering Problems.}
	\label{algo:covering}
\end{algorithm}



