%!TEX root = ./main.tex

%\section*{Appendix}
\section{Missing proofs in \Cref{sec:covering}}

\setcounter{lemma}{0}
\begin{lemma}
Following the preprocessing procedure, we can always obtain the solutions $\hat{s}_{i,k}^{t}$ such that
$\hat{s}_{i,k}^{t} \leq s_{i,k}^{t}$ and $\sum_{i=1}^{n} a_{i}^{t} \hat{s}_{i,k}^{t} = 1$. (Proof in the supplementary file.)
\end{lemma}
%
\begin{proof}
Let us fix an expert $k$. We prove the lemma by induction. At time step $t=1$, one can always scale down the solution $s_{i,k}^{1} \geq 0$ such that the first constraint becomes tight.
Assume that the lemma holds until $t-1$, $\sum_{i=1}^{n} a_{i}^{t-1} \hat{s}_{i,k}^{t-1} = 1$ and $\hat{s}_{i,k}^{t-1} \leq s_{i,k}^{t-1}$.
Consider time $t$. If after scaling down (at the first step in the procedure) the $t^{\text{th}}$ constraint becomes tight, then we are done. Otherwise, we have
	%
	\begin{align*}
		1 &< \sum_{i=1}^{n} a_{i}^{t} s_{i,k}^{t} = \sum_{i \in I} a_{i}^{t} s_{i,k}^{t} + \sum_{i \notin I} a_{i}^{t} s_{i,k}^{t}, \\
		%
		1 &= \sum_{i=1}^{n} a_{i}^{t-1} \hat{s}_{i,k}^{t-1} =  \sum_{i = 1}^{n} a_{i}^{t} \biggl( \hat{s}_{i,k}^{t-1} \cdot \frac{a_{i}^{t-1}}{a_{i}^{t}} \biggr)
		\geq  \sum_{i \in I} a_{i}^{t} \biggl( \hat{s}_{i,k}^{t-1} \cdot \frac{a_{i}^{t-1}}{a_{i}^{t}} \biggr)
		+ \sum_{i \notin I} a_{i}^{t} s_{i,k}^{t}.
	\end{align*}
	%
	Hence, there exists $\hat{s}_{i,k}^{t} \in \bigl[ \hat{s}_{i,k}^{t-1} \cdot \frac{a_{i}^{t-1}}{a_{i}^{t}}, s_{i,k}^{t} \bigr]$ for every $i$, where $1 \leq i \leq n$, such that $\sum_{i=1}^{n} a_{i}^{t} \hat{s}_{i,k}^{t} = 1$.
\end{proof}


\begin{lemma}
The $x_{i}^{t}$ solutions set by the algorithm for the original covering problem and the dual variables $(\alpha^{t}, \beta_{i}^{t})$ of the \texttt{LIN-COMB} benchmark's linear program relaxation are feasible. (Proof in the supplementary file.)
\end{lemma}
%
\begin{proof}
We first prove that the $x_{i}^{t}$ variables satisfy the covering constraints by induction. At time 0, no constraint has been released yet, and every variable is set to 0. This all-zero solution is feasible. Let us assume that the algorithm provides feasible solutions up to time $t-1$. At time $t$, the algorithm maintains the inequality $x_{i}^{t} \geq x_{i}^{t-1}$, so all constraints $t'$ where $t' < t$ are satisfied. Besides, $x_{i}^{t}$ is always at least
$\sum_{k} w_{i,k}^{t} s_{i,k}^{t}$, which is larger than $\sum_{k} w_{i,k}^{t} \hat{s}_{i,k}^{t}$ since $s_{i,k}^{t} \geq \hat{s}_{i,k}^{t}$
for all $i,k$ by the preprocessing step. Hence, the constraint $t$ is also satisfied, formally,
$$
\sum_{i=1}^{n} a_{i}^{t} x_{i}^{t}  \geq \sum_{i=1}^{n} a_{i}^{t} \biggl( \sum_{k} \hat{s}_{i,k}^{t} w_{i,k}^{t} \biggr) \geq 1.
$$

In the remaining part of the proof, we show the feasibility of $\alpha^{t}$ and every $\beta_{i}^{t}$.
Since $ \gamma^{t} \geq 0$ and $\lambda_{i}^{t} \geq 0$ for all $i$ and $t$, we get that $\alpha^{t} \geq 0$.
In the definition of  $\beta_{i}^{t}$, the nominator of the logarithm term is always larger than the denominator, and it is smaller than $K\rho$ times the denominator. Consequently, $0 \leq \beta_{i}^{t} \leq c_{i}$. Furthermore,
%
\begin{align*}
    \beta_{i}^{t+1} - \beta_{i}^{t}
    	&= - \frac{1}{\ln(K\rho)} c_i \ln \left( \frac{\sum_{k=1}^{K}  s_{i,k}^{t} w_{i,k}^{t} + \delta_{i}^{t}}{\sum_{k=1}^{K}  s_{i,k}^{t-1}w_{i,k}^{t-1} + \delta_{i}^{t-1}} \right).
\end{align*}
%
Since $\sum_{i} a_{i}^{t} \hat{s}_{i,k}^{t} = 1$, using the KKT conditions, we get:
\begin{align*}
\alpha^{t} &+ \sum_{i=1}^{n} s_{ik}^{t} \left(\beta_{i}^{t+1} - \beta_{i}^{t}\right) \\
%
&= \frac{1}{\ln(K\rho)} \biggl( \gamma^{t} + \sum_{i} \lambda_{i}^{t} \biggr)
	- \frac{1}{\ln(K\rho)}  \sum_{i=1}^{n} s_{i,k}^{t} c_i \ln \left( \frac{\sum_{k=1}^{K}  s_{ik}^{t} w_{i,k}^{t} + \delta_{i}^{t}}{\sum_{k=1}^{K}  s_{ik}^{t-1}w_{i,k}^{t-1} + \delta_{i}^{t-1}} \right) \\
%
&= \frac{1}{\ln(K\rho)} \biggl[ \gamma^{t} + \sum_{i=1}^{n} \lambda_{i}^{t} - \sum_{i=1}^{n} \left( a_{i}^{t} \hat{s}_{i,k}^{t} \gamma^{t} + \lambda_{i}^{t} + s_{i,k}^{t} \mu_{i}^{t} \right) \biggr] \\
%
&\leq 0
\end{align*}
\end{proof}
